Spin canonical rings of log stacky curves

### 2015-07-13 curves-write-up/spin-cring.tex
some edits to congruence example

If $\Gamma$ has no nonzero odd weight modular forms, then $\Gamma$ is generated in weight at most $6$ with relations in weight at most $12$. This follows in the case $g > 0$ from Voight and Zureick-Brown \cite[Theorem 1.4]{vzb:stacky} and in the case that $g = 0$ from \cite[Theorem 9.3.1]{vzb:stacky}. Note that when $g = 0$ the exceptional cases of \cite[Theorem 9.3.1]{vzb:stacky} do not occur because $\delta > 0$.

Furthermore, if $\Gamma$ has some nonzero odd weight modular form, then it must 
have no points with stabilizer order 2 by Remark ~\ref{rem:odd-denom}. 
Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is 
generated in degree at most $5$ with relations in degree at most $10$. In fact, it is not difficult to show $M(\Gamma)$ is generated in weight at most 4 with relations in weight at most 8 when the genus of the stacky curve associated to $\Gamma \backslash \BH^*$ is 0 or 1, as noted in Remark ~\ref{rem:cusp-generation-4}. Note that the exceptional cases in Tables ~\ref{table:g-1-exceptional} and ~\ref{table:g-0-exceptional} do not occur because $\Gamma$ has a cusp, so $\delta > 0$.
\end{example}

>>>>

If $\Gamma$ has no nonzero odd weight modular forms, then $\Gamma$ is generated in weight at most $6$ with relations in weight at most $12$. This follows from work by Voight and Zureick-Brown \cite[Theorem 1.4]{vzb:stacky}. Note that the exceptional cases of their result \cite[Theorem 9.3.1]{vzb:stacky}, which happen when the genus is zero, do not occur because $\delta > 0$.

If $\Gamma$ has some nonzero odd weight modular form, then it must 
have no points with stabilizer order 2 by Remark ~\ref{rem:odd-denom}. 
Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is 
generated in degree at most $5$ with relations in degree at most $10$. Furthermore, it is not difficult to show that $M(\Gamma)$ is generated in weight at most 4 with relations in weight at most 8 when the genus of the stacky curve associated to $\Gamma \backslash \BH^*$ is 0 or 1, as noted in Remark ~\ref{rem:cusp-generation-4}. Note that the exceptional cases in Tables ~\ref{table:g-1-exceptional} and ~\ref{table:g-0-exceptional} do not occur because $\Gamma$ has a cusp, so $\delta > 0$.
\end{example}
